Coherent optical association of a single molecule

### 2020-10-12 paper.tex
Update affiliation

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Kenneth Wang}
\author{J. D. Hood}
\author{Lewis Picard}
\author{Jessie T. Zhang}
\author{William Cairncross}
\author{Jeremy Hutson}
\author{Till Rosenband}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8 \mathrm{G}$
  and lifetime up to $1 \mathrm{ms}$ with more than $60\%$ of the molecule created in the
  motional ground state.
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom. \textcolor{blue}{Yichao, can you update numbers in the abstract? also, can you update affiliations in the author list, Jeremy is Durham and Jon is Purdue}
\end{abstract}

>>>>

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Kenneth Wang}
\author{J. D. Hood}
\altaffiliation{Department of Chemistry, Purdue University, West Lafayette, Indiana, 47907, USA}
\author{Lewis Picard}
\author{Jessie T. Zhang}
\author{William Cairncross}
\author{Jeremy Hutson}
\altaffiliation{Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8 \mathrm{G}$
  and lifetime up to $1 \mathrm{ms}$ with more than $60\%$ of the molecule created in the
  motional ground state.
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}
